\bf Model Visualization Techniques for a Social Network Model

### 2017-03-15 paper.Rnw
am work

<<alldataviz, fig.cap="The smaller friendship network data we will be modelling throughout the paper.", fig.width=8>>=
actual1 <- merge(data.frame(as.edgelist(as.network(fd2.w1))), 
                 data.frame(id = 1:16, drink = drink2[,1]),
                 by.x = "X1", by.y = "id", all = T)
actual1$Wave <- 1 
actual2 <- merge(data.frame(as.edgelist(as.network(fd2.w2))),
                 data.frame(id = 1:16,drink = drink2[,2]),
                 by.x = "X1", by.y = "id", all = T)
actual2$Wave <- 2
actual3 <- merge(data.frame(as.edgelist(as.network(fd2.w3))),
                 data.frame(id = 1:16,drink = drink2[,3]),
                 by.x = "X1", by.y = "id", all = T)
actual3$Wave <- 3
alldat <- rbind(actual1, actual2, actual3)
alldat$X1 <- paste0("V", alldat$X1)
alldat$X2 <- ifelse(!is.na(alldat$X2), paste0("V", alldat$X2), NA)
ggplot(data = alldat, 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink), group = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = 'fruchtermanreingold', size = 3, arrowsize = .5, arrowgap = .03) +
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  theme_net() +
  facet_wrap(~Wave, labeller = "label_both") + 
  theme(legend.position = 'bottom', panel.background = element_rect(fill = NA, color = "grey30"))
@

@@

The first vizualization we present here is an animation of microsteps simulated to emulate the transition steps from wave 1 to wave 2 the subset of the friends data shown in Figure ~\ref{fig:alldataviz}. When each ego node is selected in a microstep, it is emphasized in the animation, then the associated edge either appears or disappears. If there are no changes at a particular microstep, no changes are seen. Some frames of the animations are shown in INSERT STATIC FIGURE, and the full movie can be viewed at INSERT LINK TO GIF.

@@

We also explore simulations from these different models given parameter values. Using the means from the 1,000 fitted parameter values, we simulated 1,000 observations from each of our three models. We condition on the first friendship network observation, and the second and third observations are simulated from the SAOM models estimated previously. From these simulations, we first create a visualization that represents an ``average" network, we count occurences of each possible edge in the simulations, resulting in a summary network of simulations.

<<averagenet>>=
library(RSiena)
library(tidyverse)
#friend.data.w1 <- as.matrix(read.table("s50_data/s50-network1.dat"))
#friend.data.w2 <- as.matrix(read.table("s50_data/s50-network2.dat"))
#friend.data.w3 <- as.matrix(read.table("s50_data/s50-network3.dat"))
#drink <- as.matrix(read.table("s50_data/s50-alcohol.dat"))
friendshipData <- array(c(fd2.w1, fd2.w2, fd2.w3), dim = c(16, 16, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
library(netvizinf)
data(M1ests_bigfriends)
M1parms <- (means %>% filter(Model == "M1"))$means
M1sims1000 <- saom_simulate(dat = mydata, struct = M1eff,
                       parms = as.numeric(M1parms), N = 1000)
M1simsdf <- sims_to_df(M1sims1000)
M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))

library(geomnet)
M1avg$from <- paste0("V", M1avg$from)
M1avg$to <- paste0("V", M1avg$to)
M1avg2$from <- paste0("V", M1avg2$from)
M1avg2$to <- paste0("V", M1avg2$to)

wave2drink <- drink2[,2]
wave2drink <- as.data.frame(wave2drink)
wave2drink$id <- paste0("V", 1:16)
names(wave2drink)[1] <- "drink"
M1avgcov <- merge(M1avg, wave2drink, by.x = "from", by.y = "id", all = T)
library(tidyr)
M1avg[,-3] %>% spread(to, weight) %>% data.frame-> distmat
rownames(distmat) <- distmat$from
distmat <- distmat[,-1]
distmat <- as.matrix(sqrt(1/distmat))
distmat[is.na(distmat)] <- 0
ggplot(data = M1avgcov) + # edge appears > 50% of the time. (is this actually what that is????) 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/251, color = as.factor(drink)), 
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmat)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  scale_size_continuous(name = "Weight") + 
  theme_net()
M1avg2$wave <- M1avg2$wave + 1
alldrink <- data.frame(drink2[,2:3])
alldrink <- gather(alldrink, wave,drink) %>% mutate(wave = parse_number(wave), id = rep(paste0("V",1:16),2))

M1avg2cov <- merge(M1avg2, alldrink, by.x = c("from", "wave"), by.y = c("id", "wave"), all = T)
ggplot(data = M1avg2cov) + # edge appears > 50% of the time. (is this actually what that is????) 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/388, color = as.factor(drink)), 
           directed = TRUE, curvature = .2, labelon = F,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai", fiteach = T,
           layout.par = list(elen = distmat)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  facet_wrap(~wave, labeller = "label_both") + theme_net() + labs(title = "Average Wave 2 and Wave 3 Networks from Model M1")
# ggplot(data = M1avg %>% filter(weight >= 51)) + 
#   geom_net(aes(from_id = from, to_id = to, linewidth = weight/500), 
#            #directed = TRUE,
#            layout.alg = "mds", 
#            layout.par = list(var = 'user', dist = 'none', exp = 3,vm = distmat))

>>>>

<<alldataviz, fig.cap="The smaller friendship network data we will be modelling throughout the paper.", fig.width=8>>=
actual1 <- merge(data.frame(as.edgelist(as.network(fd2.w1))), 
                 data.frame(id = 1:16, drink = drink2[,1]),
                 by.x = "X1", by.y = "id", all = T)
actual1$Wave <- 1 
actual2 <- merge(data.frame(as.edgelist(as.network(fd2.w2))),
                 data.frame(id = 1:16,drink = drink2[,2]),
                 by.x = "X1", by.y = "id", all = T)
actual2$Wave <- 2
actual3 <- merge(data.frame(as.edgelist(as.network(fd2.w3))),
                 data.frame(id = 1:16,drink = drink2[,3]),
                 by.x = "X1", by.y = "id", all = T)
actual3$Wave <- 3
alldat <- rbind(actual1, actual2, actual3)
alldat$X1 <- paste0("V", alldat$X1)
alldat$X2 <- ifelse(!is.na(alldat$X2), paste0("V", alldat$X2), NA)
alldataviz <- ggplot(data = alldat, 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink), group = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = 'fruchtermanreingold', size = 3, arrowsize = .5, arrowgap = .03) +
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  theme_net() +
  facet_wrap(~Wave, labeller = "label_both") + 
  theme(legend.position = 'bottom', panel.background = element_rect(fill = NA, color = "grey30"))
alldataviz
@

@@

The first vizualization we present here is an animation of microsteps simulated to emulate the transition steps from wave 1 to wave 2 the subset of the friends data shown in Figure ~\ref{fig:alldataviz}. When each ego node is selected in a microstep, it is emphasized in the animation, then the associated edge either appears or disappears. If there are no changes at a particular microstep, no changes are seen. Some frames of the animations are shown in INSERT STATIC FIGURE OF THE 5-6 DIFFERENT MICROSTEPS AND ONE TRANSITION SET, and the full movie can be viewed at INSERT LINK TO GIF.

@@

We also explore simulations from these different models given parameter values. Using the means from the 1,000 fitted parameter values, we simulated 1,000 observations from each of our three models. We condition on the first friendship network observation, and the second and third observations are simulated from the SAOM models estimated previously. From these simulations, we first create a visualization that represents an ``average" network. To do this, we count occurences of each possible edge in the simulations, resulting in a summary network with weighted edges representing the number of times an edge appeared when simulating from the SAOM.

<<averagenet>>=
library(RSiena)
library(tidyverse)
#friend.data.w1 <- as.matrix(read.table("s50_data/s50-network1.dat"))
#friend.data.w2 <- as.matrix(read.table("s50_data/s50-network2.dat"))
#friend.data.w3 <- as.matrix(read.table("s50_data/s50-network3.dat"))
#drink <- as.matrix(read.table("s50_data/s50-alcohol.dat"))
friendshipData <- array(c(fd2.w1, fd2.w2, fd2.w3), dim = c(16, 16, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
M2eff <- includeEffects(M1eff, jumpXTransTrip, interaction1 = "alcohol")
M3eff <- includeEffects(M1eff, nbrDist2twice)
library(netvizinf)
data(M1ests_bigfriends)
M1parms <- (means %>% filter(Model == "M1"))$means
M2parms <- (means %>% filter(Model == "M2"))$means
M3parms <- (means %>% filter(Model == "M3"))$means
M1sims1000 <- saom_simulate(dat = mydata, 
                            struct = M1eff,
                       parms = as.numeric(M1parms), 
                       N = 1000)
M2sims1000 <- saom_simulate(dat = mydata, 
                            struct = M2eff,
                       parms = as.numeric(M2parms), 
                       N = 1000)
M3sims1000 <- saom_simulate(dat = mydata, 
                            struct = M3eff,
                       parms = as.numeric(M3parms), 
                       N = 1000)
M1simsdf <- sims_to_df(M1sims1000)
M2simsdf <- sims_to_df(M2sims1000)
M3simsdf <- sims_to_df(M3sims1000)
M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avgW2 <- M1simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M2avg <- M2simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M2avgW2 <- M2simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M2avg2 <- M2simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M3avg <- M3simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M3avgW2 <- M3simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M3avg2 <- M3simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))

library(geomnet)
M1avg$from <- paste0("V", M1avg$from)
M1avg$to <- paste0("V", M1avg$to)
M1avg2$from <- paste0("V", M1avg2$from)
M1avg2$to <- paste0("V", M1avg2$to)
M1avgW2$from <- paste0("V", M1avgW2$from)
M1avgW2$to <- paste0("V", M1avgW2$to)
M2avg$from <- paste0("V", M2avg$from)
M2avg$to <- paste0("V", M2avg$to)
M2avgW2$from <- paste0("V", M2avgW2$from)
M2avgW2$to <- paste0("V", M2avgW2$to)
M2avg2$from <- paste0("V", M2avg2$from)
M2avg2$to <- paste0("V", M2avg2$to)
M3avg$from <- paste0("V", M3avg$from)
M3avg$to <- paste0("V", M3avg$to)
M3avgW2$from <- paste0("V", M3avgW2$from)
M3avgW2$to <- paste0("V", M3avgW2$to)
M3avg2$from <- paste0("V", M3avg2$from)
M3avg2$to <- paste0("V", M3avg2$to)

wave2drink <- drink2[,2]
wave2drink <- as.data.frame(wave2drink)
wave2drink$id <- paste0("V", 1:16)
names(wave2drink)[1] <- "drink"
wave3drink <- drink2[,3]
wave3drink <- as.data.frame(wave3drink)
wave3drink$id <- paste0("V", 1:16)
names(wave3drink)[1] <- "drink"
M1avgcov <- merge(M1avg, wave2drink, by.x = "from", by.y = "id", all = T)
M2avgcov <- merge(M2avg, wave2drink, by.x = "from", by.y = "id", all = T)
M3avgcov <- merge(M3avg, wave2drink, by.x = "from", by.y = "id", all = T)
M1avgW2cov <- merge(M1avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
M2avgW2cov <- merge(M2avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
M3avgW2cov <- merge(M3avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
library(tidyr)
M1avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM1
rownames(distmatM1) <- distmatM1$from
distmatM1 <- distmatM1[,-1]
distmatM1 <- as.matrix(sqrt(1/distmatM1))
distmatM1[is.na(distmatM1)] <- 0
M1avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM1W2
rownames(distmatM1W2) <- distmatM1W2$from
distmatM1W2 <- distmatM1W2[,-1]
distmatM1W2 <- as.matrix(sqrt(1/distmatM1W2))
distmatM1W2[is.na(distmatM1W2)] <- 0
M2avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM2
rownames(distmatM2) <- distmatM2$from
distmatM2 <- distmatM2[,-1]
distmatM2 <- as.matrix(sqrt(1/distmatM2))
distmatM2[is.na(distmatM2)] <- 0
M2avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM2W2
rownames(distmatM2W2) <- distmatM2W2$from
distmatM2W2 <- distmatM2W2[,-1]
distmatM2W2 <- as.matrix(sqrt(1/distmatM2W2))
distmatM2W2[is.na(distmatM2W2)] <- 0
M3avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM3
rownames(distmatM3) <- distmatM3$from
distmatM3 <- distmatM3[,-1]
distmatM3 <- as.matrix(sqrt(1/distmatM3))
distmatM3[is.na(distmatM3)] <- 0
M3avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM3W2
rownames(distmatM3W2) <- distmatM3W2$from
distmatM3W2 <- distmatM3W2[,-1]
distmatM3W2 <- as.matrix(sqrt(1/distmatM3W2))
distmatM3W2[is.na(distmatM3W2)] <- 0

library(RColorBrewer)
cols <- brewer.pal(n = 4, "YlOrRd")

plotM1W2 <- ggplot(data = M1avgcov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/251, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM1)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  #labs(title = "Wave 2, M1") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM1W3 <- ggplot(data = M1avgW2cov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/388.5, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM1W2)
           ) + 
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  #labs(title = "Wave 3, M1") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM2W2 <- ggplot(data = M2avgcov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/325, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM2)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  #labs(title = "Wave 2, M2") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM2W3 <- ggplot(data = M2avgW2cov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/357, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM2W2)
           ) + 
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  #labs(title = "Wave 3, M2") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM3W2 <- ggplot(data = M3avgcov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/258, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM3)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  #labs(title = "Wave 2, M3") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM3W3 <- ggplot(data = M3avgW2cov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/372.5, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM3W2)
           ) + 
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  #labs(title = "Wave 3, M3") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))

origW1 <- ggplot(data = alldat %>% filter(Wave==1), 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = "kamadakawai", size = 3, arrowsize = .5, curvature = .2,
           arrowgap = .03) +
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  theme_net() +
  theme(legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
origW2 <- ggplot(data = alldat %>% filter(Wave==2), 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = "kamadakawai", size = 3, arrowsize = .5, curvature = .2,
           arrowgap = .03) +
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  theme_net() +
  theme(legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
origW3 <- ggplot(data = alldat %>% filter(Wave==3), 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = "kamadakawai", size = 3, arrowsize = .5, curvature = .2,
           arrowgap = .03) +
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  theme_net() +
  theme(legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))

library(gridExtra)
library(cowplot)
plot_grid(plot.mpg, plot.diamonds, labels = c("A", "B"), nrow = 2, align = "v")
grid.arrange(origW2, plotM1W2,
              plotM2W2,plotM3W2, 
              ncol=2, clip = T)
alldataviz2 <- alldataviz + theme(legend.position = 'none')
ggdraw() +
  draw_plot(alldataviz2, x=0, y=.75, width=1, height=.25) + 
  draw_plot(plotM1W2, .1, .5, .5, .25) +
  draw_plot(plotM1W3, .3, .5, .5, .25) +
  draw_plot(plotM2W2, .1, .25, .5, .25) +
  draw_plot(plotM2W3, .3, .25, .5, .25) +
  draw_plot(plotM3W2, .1, 0, .5, .25) +
  draw_plot(plotM3W3, .3, 0, .5, .25) + 
  draw_plot_label(label = c("Original Data", "M1: Wave 2", "M1: Wave 3", "M2: Wave 2", "M2: Wave 3", "M3: Wave 2", "M3: Wave 3"))

M1avg2$Model <- "M1"
M2avg2$Model <- "M2"
M3avg2$Model <- "M3"
allavg <- rbind(as.data.frame(M1avg2), 
                as.data.frame(M2avg2),
                as.data.frame(M3avg2))

ggplot(data = allavg) + 
  geom_histogram(aes(x = wt)) + 
  facet_grid(wave~Model) + 
  labs(x = "Number of times an edge occurs in 1,000 simulations") +
  theme_bw()

# ggplot(data = M3avgcov) + 
#   geom_net(aes(from_id = from, to_id = to, linewidth = weight/251, color = as.factor(drink)), 
#            directed = TRUE, curvature = .2,
#            ealpha = .75,
#            layout.alg = "kamadakawai",
#            layout.par = list(elen = distmatM2)
#            ) + 
#   scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
#   scale_size_continuous(name = "Weight") + 
#   theme_net()
# M1avg2$wave <- M1avg2$wave + 1
# alldrink <- data.frame(drink2[,2:3])
# alldrink <- gather(alldrink, wave,drink) %>% mutate(wave = parse_number(wave), id = rep(paste0("V",1:16),2))

# M1avg2cov <- merge(M1avg2, alldrink, by.x = c("from", "wave"), by.y = c("id", "wave"), all = T)
# ggplot(data = M1avg2cov) + # edge appears > 50% of the time. (is this actually what that is????) 
#   geom_net(aes(from_id = from, to_id = to, linewidth = weight/388, color = as.factor(drink)), 
#            directed = TRUE, curvature = .2, labelon = F,
#            #layout.alg = "fruchtermanreingold"
#            layout.alg = "kamadakawai", fiteach = T,
#            layout.par = list(elen = distmat)
#            ) + 
#   scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
#   facet_wrap(~wave, labeller = "label_both") + theme_net() + labs(title = "Average Wave 2 and Wave 3 Networks from Model M1")
# ggplot(data = M1avg %>% filter(weight >= 51)) + 
#   geom_net(aes(from_id = from, to_id = to, linewidth = weight/500), 
#            #directed = TRUE,
#            layout.alg = "mds", 
#            layout.par = list(var = 'user', dist = 'none', exp = 3,vm = distmat))
